---
title: Project Management
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/drg.R")
```

## Dynamic report generation
The script, `drg.R`, is used to compile reports in various formats based on project **R** and/or Rmd files.
Using this project management project as an example, markdown and html files are generated for existing Rmd files.
This is not clear from the code below because `output_format="all"` is ambiguous.
In the yaml front-matter of each Rmd file for this project, the file type `html_document:` and specific flag `keep_md: true` are specified.

No other output files are specified such as pdf.
To make pdf files for example, they would be specified directly in this script or the Rmd front-matter would have to be updated to include them.
I prefer to keep them separate because I rarely want to generate pdf files from most Rmd files and when I do I will want them written to another location.

## R code

### Initial setup

```{r setup}
```

### Render documents

```{r save}
```
