---
title: Project Management
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, messages=FALSE, warnings=FALSE)
read_chunk("../../code/example.R")
```

## Example usage
This is how `projman` functions can be used to create and manipulate a project, using the `projman` project itself as an example.
The code below is not intended to be run directly, but serves as a guide.

## R code

### Create a project
Note that I use my own default path for storing a project when creating a new project.
See the `projman` [default objects](objects.html "default objects") and [creating a new project](func_new.html "new project") for more details.

```{r ex_create_project}
```

### Update a project
Functions can be used to create, read, or update. See [Rmd-related functions](func_rmd.html "Rmd-related functions").

```{r ex_update_project}
```

### Prepare a project website
With some additional project-specific setup, files can be generated which will assist in creating a project website.
See [website-related functions](func_website.html "website-related functions").

```{r ex_website}
```
