---
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/projman.R")
```

#### genNavbar

`genNavbar` generates a navigation bar for a web page.
The html file created is generally written to the project's `docs/Rmd/include` directory.
However, if this function is used to create a navbar for a Github user web page, the html file should be stored in a sensible location inside the user pages repository, e.g., `leonawicz.github.io/assets`.

The common navigation bar html is included at the beginning of the body of the html for each web page in the project's website.
`menu` is a vector of names for each dropdown menu.
`submenus` is a list of vectors of menu options corresponding to each menu.
`files` is a similar list of vectors.
Each element is either an html file for a web page to be associated with the submenu link,
"header" to indicate the corresponding name in `submenus` is only a group label and not a link to a web page,
or "divider" to indicate placement of a bar for separating groups in a dropdown menu.

`theme` can be either `united` (default) or `cyborg`.
Both are from Bootswatch.
The function must apply some internal differentiation in the construction of the html navigation bar between themes.
This is currently the only `projman` function which attempts to handle multiple Bootswatch themes with different CSS tags.

```{r fun_genNavbar}
```

#### genOutyaml

`genOutyaml` generates the `_out.yaml` file for yaml front-matter common to all html files in the project website.
The file should be written to the project's `docs/Rmd` directory.
`lib` specifies the library directory for any associated files.
yaml `includes` for external html common to all project web pages in the site can also be specified with `header`, `before_body`, and `after_body`.
These can be specified by file basename only (no path) and the function assumes these files are in the `docs/Rmd/include` directory.
At this time all external libraries must be provided by the user, for example in `docs/Rmd/libs`.
It is recommended. See the project repo [gh-pages](https://github.com/leonawicz/ProjectManagement/tree/gh-pages "gh-pages") branch for an example.

```{r fun_genOutyaml}
```
