---
title: Project Management
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/pm.R")
```

##
##
## Example usage
This is how `rpm` functions can be used to create and manipulate a project, using the `rpm` project itself as an example.
The code below is not intended to be run in full directly, but serves as a guide.

### Dynamic report generation
The script, `pm.R`, is used to compile web sites and reports in various formats based on project documentation, namely Rmd files.
Using this project management project as an example, markdown and html files are generated for existing Rmd files.
There is also optional conversion from Rmd to Rnw and subsequent PDF generation.

### Github user website
Although not a part of the `pm.R` scripts associated with other **R** projects,
this example also includes creation of my Github user website, `leonawicz.github.io`, as part of overall project management.
This is in addition to the `rpm`-specific project website.

## R code

### Create a project
Note that I use my own default path for storing a project when creating a new project.
See the `rpm` [default objects](objects.html "default objects") and [creating a new project](func_new.html "new project") for more details.

```{r ex_create_project}
```

### Update a project
Functions can be used to create, read, or update. See [Rmd-related functions](func_rmd.html "Rmd-related functions").

```{r ex_update_project}
```

### Prepare a project website
With some additional project-specific setup, files can be generated which will assist in creating a project website.
See [website-related functions](func_website.html "website-related functions").

```{r ex_website}
```

### Knit documents
Both Rmd and Rnw files can be knitted to various formats.
Rmd and Rnw files can also be converted back and forth, with notable limitations.
Files can be reorganized after knitting.

```{r knit_setup}
```

```{r save}
```

### Prepare a Github user website
As mentioned, the same functions can be applied to the generation of a Github user account website just as they are used to build individual project sites.
I am currently using two somewhat incompatible bootstrap CSS themes for my user site vs. my project sites.
I have made some ugly "generalizations" to the code which generates container elements for each in order to accommodate this frustrating desire.
This is primarily an issue with differences in navbar construction.

I have only tested the code, and namely the navbar, with two themes, `united` and `cyborg`, and used these to generalize some of the code.
I suspect all the other common Bootswatch themes will work once I make them permissible.

```{r ex_user_website}
```
