---
title: Project Management
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/pm.R")
```

## Example usage
This is how `rpm` functions can be used to create and manipulate a project, using the `rpm` project itself as an example.
The code below is not intended to be run in full directly, but serves as a guide.

### Dynamic report generation
The script, `pm.R`, is used to compile web sites and reports in various formats based on project documentation, namely Rmd files.
Using this project management project as an example, markdown and html files are generated for existing Rmd files.
There is also optional conversion from Rmd to Rnw and subsequent PDF generation.

### Github user website
Although not a part of the `pm.R` scripts associated with other **R** projects,
this example also includes creation of my Github user website, `leonawicz.github.io`, as part of overall project management.
This is in addition to the `rpm`-specific project website.

## R code

### Create a project
Note that I use my own default path for storing a project when creating a new project.
See the `rpm` [default objects](objects.html "default objects") and [creating a new project](func_new.html "new project") for more details.

```{r ex_create_project}
```

### Update a project
Functions can be used to create, read, or update. See [Rmd-related functions](func_rmd.html "Rmd-related functions").

```{r ex_update_project}
```

### Prepare a project website
With some additional project-specific setup, files can be generated which will assist in creating a project website.
See [website-related functions](func_website.html "website-related functions").

```{r ex_website}
```
