---
title: Matt's Projects
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/proj_sankey.R")
```

##
##
## Introduction
I have begun using a Sankey diagram to illustrate various types of connections among my projects.
Here the purpose is to show the code used to create the project hierarchy graph shows elsewhere (and below).

### Motivation
I have created this diagram showing project and collaborator relationships that occur in my current work as part of this `rpm` Project Management Project.
However, this is a special case shown here.
In general, the reason for folding this type of graph into all of my individual projects as part of project management
is to show code and data relationships that exist for a specific project.
For example, `rpm` has its own code flow diagram as do my other projects.
But here the focus is on the particular project hierarchy diagram that is part of this project.

## Project hierarchy **R** code
Here is the code used to generate the current project hierarchy diagram.
Two packages are required.

```{r sankey_packages}
```

Current projects are hardcoded and are updated by hand when my work changes. A necessary evil.
This is essentially the data, consisting of both projects and collaborators.

```{r projects}
```

```{r people}
```

Directional connections must be made among project and among people and projects.
The connections are expressed by element-wise comparison of the equal-length `to` and `from` vectors.

```{r links, tidy=FALSE}
```

The vectors are combined in a data frame and the `igraph` package is used to grow the tree diagram.

```{r igraph}
```

The `rcharts` package has functionality for turning this into an interactive D3 visualization,
which is nice, particularly the mouseover interactivity, since there can be so much visual overlap among projects.
Additional javascript can be included to alter the colors.
My strengths are in **R** so I borrowed this code snippet from online,
but if you have skills with javascript and D3 you could probably do better with color control and opacity I imagine.

```{r rcharts}
```

Embed the chart in a document when rendering.

```{r sankey_embed, comment=NA, results="asis", tidy=F}
```
<style>iframe.rChart{ width: 100%; height: 840px;}</style>

